\documentclass[14pt,aspectratio=169]{beamer}

\usepackage{pgfpages}
\usepackage{fancyvrb}

\usepackage{tikz}
\usepackage{pgfplots}

\usepackage{minted}
\usemintedstyle{tango}

\usepackage{graphicx}

\usetheme{auriga}
\usecolortheme{auriga}

\setbeamercolor{background canvas}{bg=lightgray}

% define some colors for a consistent theme across slides
\definecolor{red}{RGB}{181, 23, 0}
\definecolor{blue}{RGB}{0, 118, 186}
\definecolor{gray}{RGB}{146, 146, 146}

\title{Web Development: \\ Using Color and Web Media}

\author{{\bf Gregory M. Kapfhammer}}

\institute[shortinst]{{\bf Department of Computer Science, Allegheny College}}

\begin{document}

{
  \setbeamercolor{page number in head/foot}{fg=background canvas.bg}
  \begin{frame}
    \titlepage
  \end{frame}
}

% Slide
%
\begin{frame}{Technical Question}
  %
  \hspace*{.25in}
  %
  \vspace*{.2in}
  %
  \begin{minipage}{5in}
    %
    \begin{center}
      %
      {\large How can I use HTML and CSS source code to design and implement
      multicolumn and responsive web page layouts?}
      %
    \end{center}
    %
  \end{minipage}
  %
  \vspace{2ex}
  %
  \begin{center}
    %
    \small Let's learn how to combine CSS and HTML to mobile-ready layouts for
    our web pages! We will also explore the benefits of using
    responsive web design frameworks. Make sure to review all previous content!\\
    %
  \end{center}
  %
\end{frame}

% Slide
%
\begin{frame}{Digital Representation of Images}
  %
  \begin{itemize}
    %
    \item What is digital image? Ultimately, it is individual components that
      are represented as binary numbers!
      %
      \vspace*{-.15in}
      %
    \item The fundamental components of a digital image:
      %
      \begin{itemize}
        %
        \item {\bf Raster (or Bitmap) Image}: individual components are pixels
          %
        \item {\bf Vector Image}: individual components are vector objects
          %
        \item {\bf Trade-offs}: when should you pick one of these formats?
          %
      \end{itemize}
      %
      \vspace*{-.2in}
      %
    \item The pixels of a raster image can be directly manipulated
      %
      \vspace*{-.2in}
      %
    \item Browsers often provide better support for raster images
      %
      \vspace*{-.2in}
      %
    \item But, vector images are resolution independent!
      %
  \end{itemize}
  %
\end{frame}

% Slide
%
\begin{frame}{Models for Representing Colors on the Web}
  %
  \begin{itemize}
    %
    \item We encode a color as a sequence of numbers
      %
      \vspace*{-.2in}
      %
    \item What are the benefits of encoding color as a number?
      %
      \vspace*{-.2in}
      %
    \item Popular color models for web pages:
      %
      \begin{itemize}
        %
        \item {\bf RGB}: Use the hexadecimal {\tt \#RRGGBB} format
          %
        \item {\bf CYMK}: Use cyan, magenta, yellow, and black for print
         %
        \item {\bf HSL}: Use hue, saturation, and lightness in CSS3
         %
        \item We adopt the RGB color model for web development!
         %
      \end{itemize}
      %
      \vspace*{-.25in}
      %
    \item You can also manipulate a color by changing its opacity
      %
      \vspace*{-.25in}
      %
    \item You can display colors differently through use of a gradient
      %
  \end{itemize}
  %
\end{frame}

\end{document}
